Heavy inextensible strings in the Schwarzschild geometry

### 2024-10-31 weighted_string.Rmd
more work

```{r plotstrings}

lambda <- seq(from = -0.05, to = -1.7, by = -0.1)
f <- approxfun(
    c(0,-0.1,-0.2,-0.5, -0.7, -1,  -1.4,     -1.6,-1.7),
    c(2.4,2.4, 2.1,1.5,   1.5, 1.1,  0.63, 0.3,0)
)

@@

for(l in lambda){
    points(string(r0=1.2,lambda=l,angles=seq(0,f(l),0.01)),type='l')
}

segments(1.2,0,4,0)
docolour <- function(lambda,...){
    points(string(r0=1.2,lambda=lambda,angles=seq(0,f(lambda),0.01)), type='l', lwd=3, ...)
}
docolour(-0.05,col='blue')
docolour(-0.7,col='green')
docolour(-1.4,col='red')
points(1.2,0,pch=16)

```

>>>>

```{r plotstringsonepointtwo}

dist <- 1.2
lambda <- seq(from = -0.05, to = -1.7, by = -0.1)
f <- approxfun(
    c(0,-0.1,-0.2,-0.5, -0.7, -1,  -1.4,     -1.6,-1.7),
    c(2.4,2.4, 2.1,1.5,   1.5, 1.1,  0.63, 0.3,0)
)

@@

for(l in lambda){
    points(string(r0 = dist, lambda = l, angles = seq(0,f(l),0.01)), type = 'l')
}

segments(dist,0,4,0)
docolour <- function(lambda,...){
    points(string(r0 = dist, lambda = lambda, angles=seq(0,f(lambda),0.01)), type='l', lwd=3, ...)
}
#docolour(-0.05,col='blue')
#docolour(-0.7,col='green')
#docolour(-1.4,col='red')
points(1.2,0,pch=16)
```

```{r plotstringsonepointzerofour}

dist <- 1.04
lambda <- seq(from = 0, to = -1, by = -0.1)

f <- approxfun(
    c(0,-0.1,-0.2,-0.5, -0.7, -1,  -1.4,     -1.6,-1.7),
    c(2.4,2.4, 2.1,1.5,   1.5, 0.5,  0.63, 0.3,0)
)

for(l in lambda){
    points(string(r0 = dist, lambda = l, angles = seq(0,f(l),0.01)), type = 'l')
}

segments(dist,0,4,0)
docolour <- function(lambda,...){
    points(string(r0 = dist, lambda = lambda, angles=seq(0,f(lambda),0.01)), type='l', lwd=3, ...)
}
docolour(0,col='red')
docolour(-1,col='blue')
points(dist,0,pch=16)
```
